A decentralized network support middleware for MMOGs

### 2009-09-15 trunk/textos/PlanoDoutorado/Lugano/planodoc_lugano.tex

This doctorate study plan proposes the research and creation of a novel support model for MMOGs (massively multiplayer online games), by using large-scale systems similar to those created for sharing of computing resources, such as file sharing peer-to-peer networks. Following this model, a distributed system could be formed to act as a server for an MMOG. Then, a portion of the game's communication and processing load would be delegated to each node of the server system -- more precisely, the game's virtual environment would be partitioned into regions, each of which managed by one or more server nodes. Such a system would be perceived by the players as an unique central servel to which they connect via a gateway. Upon connected, each player is seamlessly redirected to the appropriate server node. However, for such server system to work as expected, some issues must be addressed, such as maintaining the game state consistent among the different game server nodes, so each player has the same vision; management and balancing of the load assigned to the different server nodes; what to do when a node crashes or leaves the server system and, finally, how to broadcast and store the game state to the players in a distributed manner so that its most recent state can be restored even in the presence of system failures.

@@

\chapter{Plano de trabalho}

Este capítulo do plano de curso de doutorado tem como propósito detalhar os passos que vão se seguir para atingir os objetivos definidos anteriormente, desde a metodologia pretendida até o cronograma e planejamento dos créditos.

\section{Metodologia}
\label{sec:metodologia}

>>>>

This documente describes the full doctorate study plan whose part is intended to be executed in the University of Lugano, Switzerland. It proposes the research and creation of a novel support model for MMOGs (massively multiplayer online games), by using large-scale systems similar to those created for sharing of computing resources, such as file sharing peer-to-peer networks. Following this model, a distributed system could be formed to act as a server for an MMOG. Then, a portion of the game's communication and processing load would be delegated to each node of the server system -- more precisely, the game's virtual environment would be partitioned into regions, each of which managed by one or more server nodes. Such a system would be perceived by the players as an unique central servel to which they connect via a gateway. Upon connected, each player is seamlessly redirected to the appropriate server node. However, for such server system to work as expected, some issues must be addressed, such as maintaining the game state consistent among the different game server nodes, so each player has the same vision; management and balancing of the load assigned to the different server nodes; what to do when a node crashes or leaves the server system and, finally, how to broadcast and store the game state to the players in a distributed manner so that its most recent state can be restored even in the presence of system failures.

@@

\chapter{Workplan}

This section of the study plan aims to detail the steps to follow in order to achieve the objectives previously defined.

%Este capítulo do plano de curso de doutorado tem como propósito detalhar os passos que vão se seguir para atingir os objetivos definidos anteriormente, desde a metodologia pretendida até o cronograma e planejamento dos créditos.

\section{Methodology}
\label{sec:metodologia}
